On particular diameter bounds for integral point sets in higher dimensions \footnote{ This work was carried out at Voronezh State University and supported by Russian Science Foundation grant 19-11-00197. }

### 2025-02-25 AvdMomZvol_rails/Article.tex
[rails] Improve the final remarks
[rails] Edits from Zvolinsky: group the pics
[rails] Edits from Zvolinsky: group the sets
[rails] Remove two more redundant pics
[rails] Cite the most recent Lushina's work

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.5\linewidth]{picture_d21.png}
	\\
	\caption{PIPS $\mathcal{P}_8$ of cardinality 8 and diameter 21}
	\label{picture_d21.png}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=.45\linewidth]{picture_3.png}
	\\
	\caption{PIPS $\mathcal{P}_{10}$ of cardinality 10 and diameter 158}
	\label{picture_3.png}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.5\linewidth]{picture_5.png}
	\\
	\caption{PIPS $\mathcal{P}_{12}$ of cardinality 12 and diameter 297}
	\label{picture_5.png}
\end{figure}

@@

\begin{figure}[h!]
\center{\includegraphics[width=0.6\linewidth]{picture_7.png}}
\parbox{0.7\linewidth}{\caption{PIPS $\mathcal{P}_{14}$ of cardinality 14 and diameter 1273}
\label{picture_7.png}}
\end{figure}

@@

\begin{figure}[h!]
\center{\includegraphics[width=0.75\linewidth]{picture_18.png}}
\parbox{0.75\linewidth}{\caption{PIPS $\mathcal{P}_{22}$ of cardinality 22 and diameter 12296}
\label{picture_18.png}}
\end{figure}

@@

\item
$\mathcal{P}_{29} = \sqrt{154}/{1} * \{ (\pm 36708, 2520),
(\pm 138306 , 0),
(\pm 116058 , 0),
(\pm 86072 , 0),
(\pm 77616 , 0),
$

$
(\pm 60053 , 0),
(\pm 57792 , 0),
(\pm 43512 , 0),
(\pm 37758 , 0),
(\pm 35658 , 0),
(\pm 25746 , 0),
$

$
(\pm 24192 , 0),
(\pm 12656 , 0),
(\pm 4200 , 0),
(-199863 , 0)\}
$
,

@@

\begin{figure}[h!]
\center{\includegraphics[width=1\linewidth]{picture_24.png}}
\parbox{1\linewidth}{\caption{PIPS $\mathcal{P}_{28}$ of cardinality 28 and diameter 276612}
\label{picture_24.png}}
\end{figure}

@@

The source code can be obtained at https://gitlab.com/Nickkolok/ips-algo

\section{Acknowledgements}
The authors thank A.S. Usachev for his help in polishing the text of the paper.

>>>>

If a rails IPS $\mathcal P$ is contained in two parallel lines $m_1$ amd $m_2$
and $M_1,M_2 \in \mathcal P \cap m_1$, then $|M_1 M_2|\geq 3$
(the second condition is essential)~\cite{lushina2025norailswith2}.

@@

@@

\begin{figure}[h!]
	\includegraphics[width=.48\linewidth]{picture_d21.png}
	\hfill
	\includegraphics[width=.48\linewidth]{picture_3.png}
	\\
	\parbox{.48\linewidth}{\caption{PIPS $\mathcal{P}_8$ of cardinality 8 and diameter 21}
		\label{picture_d21.png}}
	\hfill
	\parbox{.48\linewidth}{\caption{PIPS $\mathcal{P}_{10}$ of cardinality 10 and diameter 158}
		\label{picture_3.png}}
\end{figure}

@@

\begin{figure}[h!]
	\includegraphics[width=.48\linewidth]{picture_5.png}
	\hfill
	\includegraphics[width=.48\linewidth]{picture_7.png}
	\\
	\parbox{.48\linewidth}{\caption{PIPS $\mathcal{P}_{12}$ of cardinality 12 and diameter 297}
		\label{picture_5.png}}
	\hfill
	\parbox{.48\linewidth}{\caption{PIPS $\mathcal{P}_{14}$ of cardinality 14 and diameter 1273}
		\label{picture_7.png}}
\end{figure}

@@

@@

@@

\item
$\mathcal{P}_{29} = \mathcal{P}_{28} \cup \sqrt{154}/{1} * \{(-199863 , 0)\}
$
,

@@

@@

The source code can be obtained at https://gitlab.com/Nickkolok/ips-algo .
The preprint of this article is arXiv:1909.10386 [math.CO]

The authors thank A.S. Usachev for his help in polishing the text of the paper.
